Deep Learning for Automatic Speech Recognition

### 2015-04-28 Paper/Paper.tex
citations added

\paragraph{} Despite how well GMMs work, deep learning approaches have overtaken them as the acoustic model for ASR applications for a few reasons. One is simply due to an increase in processing power and more refined algorithms for training and pre-training. But arguably the main reason why deep learning performance outstrips that of GMMs is due to the overall size of the models. For example, in \TODO{cite}, they use a CNN with around 60 million parameters and 650,000 neurons for image classification on the ImageNet dataset. For speech recognition, artificial neural networks are able to take in multiple frames of the acoustic context as input, while GMMs typically look at a single frame and build an expert around it. ANNs normally take in around 9-11 frames, and process the center frame around that window. This extra context allows them to take into account a variety of additional features when modeling the posterior probabilities.

@@

\TODO{Pic of input or architecture?}

\paragraph{} Over the past few years, convolutional neural networks have proven to be highly successful in image recognition tasks. Not only have they achieved the highest results on the MNIST character recognition dataset\TODO{cite}, but they've even proven to outstrip hand-crafted object recognition systems on the much more complex ImageNet dataset \TODO{cite}. This success primarily originates from the networks ability to replicate lower-resolution features across the input space. They have also previously been used for speech recognition in \TODO{cite}, but without great success. There they claim that while CNNs look promising for ASR, just taking the same structure as one built for image recognition will not suffice. For example, in that work they used convolutions performed along the time axis. \cite{DBLP:journals/taslp/Abdel-HamidMJDPY14} attempts to address these concerns and instead design a CNN specifically for ASR.

\paragraph{} Before discussing the network architecture itself, it's important to understand how the input to the model is structured. Contrary to the above DNN model, the CNN model used here does not use the standard MFCC features as input. Because these are decorrelated by the discrete cosine transform, they may not maintain the locality that is necessary for the convolutions to be meaningful. As such, they used the log-energy directly from the mel-frequency spectral coefficients, what they refer to as MFSC features, along with their deltas and delta-deltas. Also, while the DNN model used only 11 frames as input, here they use 15 frames as their input window. \cite{DBLP:journals/taslp/Abdel-HamidMJDPY14} proposes two different ways of structuring these 15 frames. These could be arranged into three 2-D feature maps with frequency on one axis and time on the other. This would allow for 2-D convolutions that normalize both frequency and time domains at the same time. Instead, they opt for the second solution where each frame is aligned into 1-D arrays across the 40 frequency bands. This results in 45 feature maps, each with 40 features. Because there are three separate feature maps for each frame, convolutions are not applied across the time domain like in \TODO{cite}, but instead relegated to the HMM part of the model. Instead, convolutions occur only along the frequency axis.

@@

\paragraph{}The pooling function used in a CNN is normally either one of \textit{averaging} or \textit{maximization}. In image processing, \TODO{cite for maxpool vs average} found that max-pooling consistently provided better results over average pooling. In this work, a max-pooling function was used throughout the network:
\begin{equation*}
p_{i,m} = \max_{n=1}^{G} q_{i, (m-1)xs+n}
\end{equation*}
where \textit{G} is the pooling size and \textit{s} is the shift size. If $G=s$, there is no overlap between pooling windows. Traditionally, these are kept from overlapping to simplify the structure of the network. \TODO{cite ImageNet} found that having slight overlaps in their pooling windows actually increased performance of their system. \cite{DBLP:journals/taslp/Abdel-HamidMJDPY14} decided to vary these two values independently to discover whether or not this held true for acoustic processing as well.

>>>>

\paragraph{} Despite how well GMMs work, deep learning approaches have overtaken them as the acoustic model for ASR applications for a few reasons. One is simply due to an increase in processing power and more refined algorithms for training and pre-training. But arguably the main reason why deep learning performance outstrips that of GMMs is due to the overall size of the models. For example, in \cite{DBLP:conf/nips/KrizhevskySH12}, they use a CNN with around 60 million parameters and 650,000 neurons for image classification on the ImageNet dataset. For speech recognition, artificial neural networks are able to take in multiple frames of the acoustic context as input, while GMMs typically look at a single frame and build an expert around it. ANNs normally take in around 9-11 frames, and process the center frame around that window. This extra context allows them to take into account a variety of additional features when modeling the posterior probabilities.

@@

\paragraph{} Over the past few years, convolutional neural networks have proven to be highly successful in image recognition tasks. Not only have they achieved the highest results on the MNIST character recognition dataset\cite{DBLP:journals/corr/abs-1003-0358}, but they've even proven to outstrip hand-crafted object recognition systems on the much more complex ImageNet dataset \cite{DBLP:conf/nips/KrizhevskySH12}. This success primarily originates from the networks ability to replicate lower-resolution features across the input space. They have also previously been used for speech recognition in \cite{hau2011exploring}, but without great success. There they claim that while CNNs look promising for ASR, just taking the same structure as one built for image recognition will not suffice. For example, in that work they used convolutions performed along the time axis. \cite{DBLP:journals/taslp/Abdel-HamidMJDPY14} attempts to address these concerns and instead design a CNN specifically for ASR.

\paragraph{} Before discussing the network architecture itself, it's important to understand how the input to the model is structured. Contrary to the above DNN model, the CNN model used here does not use the standard MFCC features as input. Because these are decorrelated by the discrete cosine transform, they may not maintain the locality that is necessary for the convolutions to be meaningful. As such, they used the log-energy directly from the mel-frequency spectral coefficients, what they refer to as MFSC features, along with their deltas and delta-deltas. Also, while the DNN model used only 11 frames as input, here they use 15 frames as their input window. \cite{DBLP:journals/taslp/Abdel-HamidMJDPY14} proposes two different ways of structuring these 15 frames. These could be arranged into three 2-D feature maps with frequency on one axis and time on the other. This would allow for 2-D convolutions that normalize both frequency and time domains at the same time. Instead, they opt for the second solution where each frame is aligned into 1-D arrays across the 40 frequency bands. This results in 45 feature maps, each with 40 features. Because there are three separate feature maps for each frame, convolutions are not applied across the time domain like in \cite{hau2011exploring}, but instead relegated to the HMM part of the model. Instead, convolutions occur only along the frequency axis.

@@

\paragraph{}The pooling function used in a CNN is normally either one of \textit{averaging} or \textit{maximization}. In image processing, \cite{DBLP:conf/icann/SchererMB10} found that max-pooling consistently provided better results over average pooling. In this work, a max-pooling function was used throughout the network:
\begin{equation*}
p_{i,m} = \max_{n=1}^{G} q_{i, (m-1)xs+n}
\end{equation*}
where \textit{G} is the pooling size and \textit{s} is the shift size. If $G=s$, there is no overlap between pooling windows. Traditionally, these are kept from overlapping to simplify the structure of the network. \cite{DBLP:conf/nips/KrizhevskySH12} found that having slight overlaps in their pooling windows actually increased performance of their system. \cite{DBLP:journals/taslp/Abdel-HamidMJDPY14} decided to vary these two values independently to discover whether or not this held true for acoustic processing as well.
